### 2016-10-05 robust-software.tex
Floating point issues

\item
Point out that even minor changes to code can cause minor changes in output
because of floating-point issues,
which means that getting exactly the same output for the same input and parameters
probably won't work during development
(but should still be a goal for people who've deployed).

@@

Given a set of parameters and a dataset, the package should produce the
same results every time it is run.

>>>>

@@

Given a set of parameters and a dataset, a particular version of a program
should produce the same results every time it is run
to aid testing, debugging, and reproducibility.
Even minor changes to code can cause minor changes in output because of floating-point issues,
which means that getting exactly the same output for the same input and parameters
probably won't work during development,
but it should still be a goal for people who have deployed a specific version.
